TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-07-13 paper/draft.tex

The model we have developed does have limitations however.
For example, it delivers chi-squared values---goodness-of-fit measures---that
are large; the model is not technically an accurate description of the spectra,
especially when the spectra are observed at signal-to-noise levels above 100.
For another, it does not include some known physical and instrumental effects.
It does not include a term or terms for line broadening from rotation or
convection (\eg, \citealt{Behmard2019}).
It does not include any accounting for binarity or superposition of multiple
stellar spectra (as in, say, \citealt{ElBadry:2010}).
And it does not include any adjustments for instrumental variations, like for
example the small but significant variations of \apogee\ resolution with
spectrograph fiber number (as are included in \citealt{Ness2018}).

@@

HOGG: Talk future work/implications with other stellar surveys (e.g. LAMOST), and exoplanet surveys (e.g. TESS)

%%==========================================================================================
\acknowledgements
We would like to acknowledge Hans Walter Rix (MPIA), Derek Homeier (Universit{\"a}t Heidelberg), Wolfgang Bradner (MPIA), Anna-Christina Eilers (MPIA), Diogo Souto (Observatário Nacional/MCTI) and Keivan Stassun (Vanderbuilt) for constructive discussions in the process of this project, as well as Bertrand Goldman (MPIA) and those who have supported the internship program at the Max Planck Institute f{\"u}r Astronomie for providing JB with funding and hospitality.
This project was partially supported by
the US National Aeronautics and Space Administration (NASA grant NNX12AI50G),
the US National Science Foundation (NSF grant AST-1517237),
and the Moore--Sloan Data Science Environment at NYU.

>>>>

The model we have developed does have limitations however.
For example, it delivers chi-squared values---goodness-of-fit measures---that
are large; the model is not technically an accurate description of the spectra,
especially when the spectra are observed at signal-to-noise levels above 100.
For another, it does not include some known physical and instrumental effects.
It does not include a term or terms for line broadening from rotation or
convection (for exmaple, \citealt{Behmard2019}).
It does not include any accounting for binarity or superposition of multiple
stellar spectra (as in, say, \citealt{ElBadry:2018}).
And it does not include any adjustments for instrumental variations, like for
example the small but significant variations of \apogee\ resolution with
spectrograph fiber number (as are included in \citealt{Ness2018}).

@@

%%==========================================================================================
\acknowledgements
We would like to acknowledge Hans Walter Rix (MPIA), Derek Homeier (Universit{\"a}t Heidelberg), Wolfgang Bradner (MPIA), Anna-Christina Eilers (MPIA), Melissa Ness (Columbia), Diogo Souto (Observatário Nacional/MCTI) and Keivan Stassun (Vanderbuilt) for constructive discussions in the process of this project, as well as Bertrand Goldman (MPIA) and those who have supported the internship program at the Max Planck Institute f{\"u}r Astronomie for providing JB with funding and hospitality.
This project was partially supported by
the US National Aeronautics and Space Administration (NASA grant NNX12AI50G),
the US National Science Foundation (NSF grant AST-1517237),
and the Moore--Sloan Data Science Environment at NYU.
